% status: 100
% chapter: SciKit Learn Algorithm

\title{ProjectProposal of REST Service Framework for Singular Value 
Decomposition on MNIST Image Classification Problem}

\author{Goutham Arra}
\affiliation{%
  \institution{Indiana University}
  \city{Bloomington} 
  \state{IN} 
  \postcode{47408}
  \country{USA}}
\email{garra@iu.edu}

\author{Priyadarshini Vijjigiri}
\affiliation{%
  \institution{Indiana University}
  \city{Bloomington} 
  \state{IN} 
  \postcode{47404}
  \country{USA}}
\email{pvijjigi@iu.edu}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{G. v. Laszewski}


\begin{abstract} 
For tasks such as image classification, Speech denoising etc..
Deep learning algorithms with complex  neural networks are being used as they
have proven more accurate in the recent  times. However, one of the downsides to
running deep learning algorithms is they can be computationally heavy and
require huge memory to execute. The solution to  the above problem is performing
Singular Value Decomposition on them.


\end{abstract}

\keywords{hid-sp18-401, hid-sp18-421, REST, Deep Learning, Neural Networks, 
tensorflow, Singular Value Decomposition. 
}


\maketitle

\section{Project Proposal}

Tensorflow is an open source machine learning framework that runs in Python to 
mainly implement Neural Network algorithms. 

MNIST classification is a famous problem in the deep learning community, which
is  nothing but classification of images into 10 categories of numbers from 0-9.
These are images with hand-written numbers on them.

MNIST data can be downloaded from the internet with direct tensorflow python
commands in our program. It contains 55000 train images on which we first train 
our neural network. The dataset also consists of 10,000 test images to test
how well our model has fared on the test images.

But running such an algorithm requires huge memory, usually GPU clusters are
used. We want to be able to run this problem on compressed network, as much as
using only  4 percent of the memory previously used. This can be done by
perfoming Singular Value Decomposition on the weight matrices of original Neural
Network.

Singular Value Decomposition is a mathematical concept where a given matrix can
be represented as product of three matrices, which are left orthogonal singular
matrix, one diagonal matrix containing singular values and one right orthogonal
singular matrix. With this kind of decomposition of weight matrices of our
original neural network, we can compress the weight matrices, by using these
three matrices and choosing only select singular values which are most
important.

By choosing the number of singular values that we want to consider, we can
compress the neural network by compromising on the test accuracy. Through this
project, we want to be able to have the option of choosing this number among the
following  - 10, 20, 50, 100, 200. Lets call this number D. For each value of 
D, we want to train the network with this compressed neural network and see 
how well it is able to predict the test images.

REST services will be implemented to perform Singular Value decomposition on 
our Neural network accorging to our chosen choice of D and train the network,
do feed forwarding of test images and display the accuracy.

Rest APIs with D = 10, 20,50, 100, 200 will be created.

~\cite{mnist}
~\cite{svd}

\section{Conclusion}

Through this project, we shall be able to compress the network for MNIST deep 
learning classification problem by applying Singular Value Decompositon on them
according to our chosen number of singular values with the help of REST services 
and APIs for each value of D.

\begin{acks}

  The authors would like to thank Dr.~Gregor~von~Laszewski for his
  support and suggestions to write this paper.

\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{report} 

